%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LAGG curriculum vitae
%
% The original template (Wilson Resume/CV) has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original authors:
% Howard Wilson (https://github.com/watsonbox/cv_template_2004) with
% extensive modifications by Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-----------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-----------------------------------------------------------------------------

\documentclass[10pt]{article} % Default font size

\input{structure.tex} % Include the file specifying document layout

%-----------------------------------------------------------------------------

\begin{document}

%-----------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%-----------------------------------------------------------------------------

\title{\href{https://br.linkedin.com/in/laggarcia}{Leonardo Garcia}} % Print the main header

%-----------------------------------------------------------------------------

\parbox{0.5\textwidth}{ % First block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Nationality} \> Brazilian \\ % Nationality
{\bf Mobile Phone} \> +55-19-99194-6670 \\ % Mobile phone
{\bf Email} \> \href{mailto:laggarcia@gmail.com}{laggarcia@gmail.com} \\ % Email address
\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second bloc
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Address} \\
Alameda das cerejas, 3 - Chácara Prado \\ % Address line 1
Campinas - SP - Brazil \\ % Address line 2
CEP: 13042-082 \\ % Address lin
\end{tabbing}}

%-----------------------------------------------------------------------------
%	PERSONAL PROFILE
%-----------------------------------------------------------------------------

\section{Personal Profile}

%Leadership and development job application
A Computer Science Master with 20+ years of experience in a variety of areas, seeking a challenging and exciting position in a multi-national, multi-cultural, world wide team working with open source to which I can contribute not only with my technical skills, but also with my leadership and soft skills. I am good at building teams and keeping them motivated over time, even through adversary situations.

%-----------------------------------------------------------------------------
%	EDUCATION SECTION
%-----------------------------------------------------------------------------

\section{Education}

\education
{Jan 2007}{Nov 2013}
{Master in Computer Science}
{University of Campinas (Unicamp)}{http://www.ic.unicamp.br/en}
{\href{http://repositorio.unicamp.br/jspui/handle/REPOSIP/275619}{Performance and energy consumption analysis and study on software transactional memories}}

%-----------------------------------------------------------------------------

\education
{Mar 1999}{Nov 2003}
{Computer Engineering}
{University of Campinas (Unicamp)}{http://www.unicamp.br/unicamp/?language=en}


%-----------------------------------------------------------------------------
%	EMPLOYMENT HISTORY SECTION
%-----------------------------------------------------------------------------

\section{Employment History}

\employer
{Jan 2022}{present}
{Linaro}{https://linaro.org}
\job
{Solutions Architect (Jan 2026 - present)}
{Worked with the sales team in pre-sales technical activities, helping to close 1 million USD in a quarter in new system software development professional service contracts for the company. Also helped to build a sales pipeline of 1.5 million USD for the following quarter.}
\job
{Chair of the Data Center Group (May 2022 - Dec 2025)}
{The Linaro Data Center Group aims to, together with its members, provide a common development center for the Arm enterprise ecosystem. Working together to resolve common issues and develop standards reduces fragmentation and helps participating companies deliver their products to market faster. As the chair of this segment group inside Linaro, I am responsible for coordinating the discussions amongst the members and making sure the group has a cohesive strategy and direction that is translated into actual projects being worked by Linaro's and its members' engineers.
}
\job
{Engineering Director (Dec 2023 - Dec 2025)}
{Responsible for all the engineering projects related to server platforms inside Linaro. Leaded the teams around the world working on enabling Confidential Computing on Arm end-to-end (from firmware to workload management), making QEMU compatible with the Arm Server Base System Architecture, porting Tensorflow, Apache Big Data and various Storage framework projects to Arm servers, and optimizing OpenSSL performance.}
\job
{Technology and Product Manager (Jan 2022 - Nov 2023)}
{As part of the Technology and Product Management team I share the responsibility to maintain the formation and articulation of a coherent strategy for all of Linaro. This is done in partnership with the Engineering team, as well as the Business Development team. My main focus has been with technologies, products and projects related to data center and servers, but I also work with a variety of other topics, including automotive and client PC.
}

\employer
{Apr 2006}{Jan 2022}
{IBM Linux Technology Center (LTC)}{http://www.ibm.com}
\job
{Open Virtualization/KVM on Power development technical leader (Jan 2013 - Jan 2022)}
{

\begin{itemize-noindent}
\item{KVM on Power development technical leader (Aug 2014 - Jan 2022): leading a team spread through many countries and multiple time zones doing community work on \href{http://www.qemu.org/}{QEMU}/\href{http://www.linux-kvm.org}{KVM}, \href{https://libvirt.org/}{libvirt}, \href{https://github.com/aik/SLOF}{SLOF}, virtio, VFIO, \href{https://github.com/kimchi-project/kimchi}{Kimchi}, and \href{https://github.com/kimchi-project/ginger}{Ginger} for Power, as well as developing and maintaining these pieces on \href{http://www-03.ibm.com/systems/power/software/linux/powerkvm/}{PowerKVM}, \href{https://open-power-host-os.github.io/}{OpenPOWER Host OS}, and IBM partners \href{https://www.redhat.com/en}{Red Hat} and \href{https://canonical.com/}{Canonical} distros.}
\item{Open Virtualization development technical leader (Jan 2013 - Aug 2014): leading a team spread through USA, Brazil, and China doing community work on \href{http://www.qemu.org/}{QEMU}/\href{http://www.linux-kvm.org}{KVM} and \href{https://github.com/kimchi-project/kimchi}{Kimchi} for x86 and cross-platform open virtualization code.}
\item{Got promoted to Senior Software Engineer while on this project. Received an IBM Outstanding Technical Achievement Award (OTAA), one of the most important technical awards inside IBM, for the work done in this project.}
\end{itemize-noindent}

}
\job
{Open Virtualization Linux distro developer and technical leader (Jan 2010 - Dec 2012)}
{Customization, build automation, and support for multiple clients using a minimal Linux distribution with virtualization support.

\begin{itemize-noindent}
\item{Developed automatic configuration of virtual machine hardware.}
\item{Developed tools to backup and restore server configuration.}
\item{Developed a VNC client that runs on top of Linux framebuffer.}
\item{Became the technical leader of this team in Jan 2011. Expanded the team to 3 countries (Brazil, USA, and China).}
\item{Got promoted to Advisory Software Engineer while on this project. Received an IBM Outstanding Technical Achievement Award (OTAA), one of the most important technical awards inside IBM, for the work done in this project.}
\end{itemize-noindent}

}
\job
{Software Engineer (Jan 2009 - Dec 2009)}
{

\begin{itemize-noindent}
\item{ServerGuide Scripting Toolkit, Linux Edition (Mar 2009 - Dec 2009): developed a tool to automatically install and configure RHEL, SLES, or VMWare ESX on x86 and Power Linux servers.}
\item{Shell Script Translator developer (Jan 2009 - Mar 2009): developed a ksh parser.}
\end{itemize-noindent}

}
\job
{Cell IDE developer and technical leader (Apr 2006 - Jan 2009)}
{Developed a C/C++ Integrated Development Environment (IDE) based on \href{https://eclipse.org/}{Eclipse} for the IBM Cell/B.E. and wire-speed Power processor.

\begin{itemize-noindent}
\item{Became the technical leader of this team in October 2007.}
\item{Integrated toolchain and performance analysis tools; developed automatic generation of makefiles.}
\item{Developed a framework for remote execution.}
\item{Responsible for Cell IDE builds.}
\item{Interacted with the Eclipse and plug-ins development community; interacted with users communities.}
\item{Contributed Cell IDE to \href{http://www.eclipse.org/ptp/}{PTP}.}
\end{itemize-noindent}

}
\job
{Other activities}
{While at IBM, got also involved with:

\begin{itemize-noindent}
\item{R\&D project manager and consultant (Mar 2009 - present): projects developed in partnerships with external R\&D institutes through Brazilian government tax exemption programs. Worked as project manager on the following projects:

\begin{itemize}
\item{Microsoft Active Directory - Samba 4 migration (Mar 2009 - Apr 2010).}
\item{Open Virtualization on Power Systems (Mar 2010 - Mar 2011): VirtIO on PowerVM.}
\end{itemize}

}
\item{Technical Recruiter (Jan 2008 - present).}
\item{Technical consultant (Jan 2008 - present): analysis and help with Linux ecosystem issues related to pre-sales, post-sales, or support situations coming from other areas of the company.}
\item{Mentorship program (Jan 2007 - present).}
\item{University Ambassador activities (Sep 2006 - Jan 2010).}
\end{itemize-noindent}

}

%-----------------------------------------------------------------------------

\employer
{Mar 2003}{Apr 2006}
{Compera (currently Movile)}{https://www.movile.com/en/}
\job
{Software support, operations, and development analyst}
{Worked on multiple fronts of Dispara, a field service management platform that integrates, through mobile devices, companies' back-offices with their field workforce. Started working on support and monitoring of the platform on customer sites and grew my responsibilities to the point I was responsible for the whole product.

\begin{itemize-noindent}
\item{Support and monitoring manager: 24x7 support and monitoring of all Dispara clients: 4500+ users all over Brazil working for 40+ companies.}
\item{Operation analyst: responsible for the operation, maintenance, up-time and performance of the Dispara platform, including the SQL Server database tuning.}
\item{Project analyst: responsible for customers' requirements analysis.}
\item{Development analyst: leader of the technical specification and integration development team; responsible for the projects, development, and deployment tasks.}
\item{Product manager: responsible for the structure, model, and development of Dispara platform new versions; integrated Dispara with multiple mobile telecoms (via SMS, UP.Notify, and WAP Push); helped to design a workflow manager.}
\end{itemize-noindent}

}

%-----------------------------------------------------------------------------

%\employer
%{Feb 2003}{Mar 2003}
%{Dextra}{http://dextra.com.br/en/}
%\job
%{Software developer intern}
%{Developed dynamic web sites based on Java (JSP and Servlets) and Perl.}

%------------------------------------------------

\employer
{Dec 2001}{Mar 2003}
{CenPRA}{http://www.cenpra.gov.br/}
\job
{Research intern}
{Worked with micro-controllers, Linux real-time kernel modules, and a Linux distribution on the Autonomous Unmanned Remote mOnitoring Robotic Airship (AURORA).

\begin{itemize-noindent}
\item{Developed software and hardware on PIC micro-controllers to get measures taken by sensors and send them through a Control Area Network (CAN).}
%\item{Integrated the visual system developed to the airship and its operating system (Real-Time Linux).}
\item{Built a Linux distribution from scratch based on Slackware that fulfilled the low memory footprint and real-time support requirements.}
\item{Ported Linux real-time kernel modules from Linux 2.0 to Linux 2.4.}
%\item{Adjusted the airship simulator for the new development platform and integration of the computer based vision system with it.}
\end{itemize-noindent}

}

%-----------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%-----------------------------------------------------------------------------

\section{Publications}

\begin{itemize}
 \item \textit{Arquitetura de Computadores: educação, ensino e aprendizado - Capítulo 5: Proposta de um Elenco de Disciplinas de Pós-Graduação para Formação de Arquitetura de Computadores.} \\
  S. T. Kofuji ; J. M. Kofuji ; M. L. Netto ; W. J. Chau ; F. Valiante Filho ; \textbf{L. A. G. Garcia} ; E. D. Moreno ; E. Horta ; E. Lima ; D. Vahia.  \\
  ISBN: 978-85-7669-263-8, 2012, Sociedade Brasileira de Computação (SBC).
 \item \textit{Energy-Performance Tradeoffs in Software Transactional Memory.} \\
  A. Baldassin ; J. P. L. de Carvalho ; \textbf{L. A. G. Garcia}, Rodolfo Azevedo. \\
  Proceedings of the 24th International Symposium on Computer Architecture and High Performance Computing (SBAC-PAD'2012).
 \item \textit{A Software Transactional Memory System for an Asymmetric Processor Architecture.} \\
  F. Goldstein ; A. Baldassin ; P. Centoducatte ; R. Azevedo ; \textbf{L. A. G. Garcia}. \\
  Proceedings of the 20th International Symposium on Computer Architecture and High Performance Computing (SBAC-PAD'08), v. 1, p. 175-182, 2008. \\
  This article received the Júlio Salek Aude prize of best paper at SBAC-PAD’08.
\end{itemize}

%-----------------------------------------------------------------------------
%	PRESENTATIONS SECTION
%-----------------------------------------------------------------------------

\section{Presentations}

\begin{itemize}
 \item \textit{Performance and energy consumption analysis and study on software transactional memories.} \\
  \textbf{L. A. G. Garcia}. \\
  Best master thesis of the Concurso de Teses e Dissertação do XV Workshop em Sistemas Computacionais de Alto Desempenho (WSCAD 2014).
 \item \textit{Análise de desempenho e consumo de energia em Memórias Transacionais.} \\
  \textbf{L. A. G. Garcia} ; A. Baldassin ; R. Azevedo. \\
  Poster presented at III Escola Regional de Alto Desempenho de São Paulo (ERAD-SP 2012).
 \item \textit{FaceID: Benchmarks for Face Detection Algorithms Using Cell Processor.} \\
  R. K. Hiramatsu ; J. M. Kofuji ; S. T. Kojufi ; L. Mattes ; \textbf{L. A. G. Garcia}. \\
  Poster at The 2nd Annual Carleton Cell BE Programming Workshop, 2009.
 \item \textit{Programando multicore com IBM full-system simulator - Cell Broadband Engine.} \\
  J. M. Kofuji ; S. T. Kojufi ; R. K. Hiramatsu ; \textbf{L. A. G. Garcia}. \\
  Presentation at the VIII Workshop em Sistemas Computacionais de Alto Desempenho (WSCAD 2007).
 \item \textit{Workshop de Programação Cell}. \\
  \textbf{L. A. G. Garcia}. \\
  Workshop at the Congresso Regional de Computação e Informática do Oeste Paulista, 2007.
\end{itemize}

%-----------------------------------------------------------------------------
%	COMPUTING SKILLS SECTION
%-----------------------------------------------------------------------------

\section{Software Engineering Skills}

\skillgroup{Programming Languages}
{
\textit{C/C++, Java, C\#, Pascal, Assembly (x86, MIPS, Motorola 68k and Microchip PIC).} \\
\textit{Python, Perl, Bash, JavaScript, VBScript.} \\
}

%-----------------------------------------------------------------------------

\skillgroup{Miscellaneous}
{
\textit{Experience with various operating systems}: Linux, Unix (Solaris, Digital), Windows. \\
\textit{Database architecture and administration}: SQL Server, Firebird. \\
\textit{Networking programming}: TCP/IP protocols (HTTP, FTP, TELNET, POP, SMTP), client-server programming, sockets, RPC, RMI, CORBA, and Web Services. \\
\textit{Knowledge about traditional and Agile development methodologies} \\
\textit{Content version control}: git, SVN, CVS. \\
}

%-----------------------------------------------------------------------------
%	LANGUAGES
%-----------------------------------------------------------------------------

\section{Languages}

\textit{Native Portuguese} \\
\textit{Proficient English} \\
\textit{Basic understanding of Spanish and French} \\

\end{document}
